testibng

### 2024-01-08 Code/R FIle.qmd

#### State Dataframes
```{r}
full_state_data <- union_states |> 
  filter(sector == "Total") |> 
  select(-sector,
         -state_abbreviation) |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 1, 0)) |> 
  left_join(minimum_wage, by = c("year", "state")) |> 
  group_by(year, state) |> 
  mutate(party_state_avaerage = mean(party_binary))
```

@@

@@

```{r}
full_ntl_data <- income_distribution |> 
  left_join(union_wages, by = "year")
```
```{r}
range(full_ntl_data$year)
```

@@

>>>>

#### State Dataframes
```{r}
full_state_data <- union_states |> 
  filter(sector == "Total") |> 
  select(-sector,
         -state) |> 
  left_join(house, by = c("year", "state_abbreviation")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 1, 0)) |> 
  left_join(minimum_wage, by = c("year", "state")) |> 
  group_by(year, state) |> 
  mutate(party_state_avaerage = mean(party_binary)) |>
  ungroup()
```

@@

```{r}
full_state_data %>% 
  ungroup %>% 
  count(year)
```

@@

##### Creating Adjusted Wages Columns

```{r}
state_to_ntl <- full_state_data |>
  ungroup() %>% 
  mutate(adjusted_wage_prop = fed_min_wage / fed_min_wage_2020_adj, .after = year) |>
  distinct(year, .keep = TRUE) 
#  select(year:adjusted_wage_prop)
```

```{r}
full_ntl_data <- income_distribution |> 
  left_join(union_wages, by = "year") |>
  mutate(decade = paste0((year - year %% 10), "s"), .after = year)
```

```{r}
range(full_ntl_data$year)
```

@@

```{r}
summary(full_ntl_data)
summary(full_state_data)
```

#### Graphing Full State Data
